---
title: "ai_with_noclosure"
author: "Sara Orofino"
date: "4/3/2020"
output: html_document
---


I want to replicate the graphs used in faculty reviews for assessment intervals but instead use the new combined data where instead of closing the fishery if it is over the limit, catch is reduced by 95%.  

I'm creating three graphs for the public presentation:

 - Graph 1: Just the individual test result with constant productivity using the proportion of healthy fisheries as y axis  
 - Graph 2: Compare the results of prop healthy for constant vs. updating productivity (but I'll change the labels)  
 - Graph 3: Compare prop healthy for constant, updating, and proxy results  

## Packages 

```{r packages-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(here)
```

## Data Constant
```{r data-c, warning = FALSE, message = FALSE}
ai_c <- read_csv(file=file.path(here(), "/analysis/no_closure/all_data/noclose_all_c.csv"))
```


## Wrangle Constant
```{r wrangle}
##Wrangling with the combined data set:
ai_intervals <- c(20,15,10,5,1) #new intervals in correct order

ai_c[is.na(ai_c)] <- "misc" #turn status NA into misc

# Calculate proportions for graphing:
ai_props_c <- ai_c %>% 
  mutate(assess_int = factor(assess, levels = ai_intervals)) %>%
  group_by(assess_int) %>%
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate(simulations = sum(over + good + misc)) %>% 
  mutate(prop_good = good / simulations)
```

## Graph 1: Constant FMSY:
```{r graph-constant}
ai_c_graph <- ggplot(ai_props_c, aes(x = assess_int, y = prop_good)) +
  geom_col(alpha = 0.8, fill = "#BC6435") + 
  theme_light()+
  coord_cartesian( ylim=c(0,1), expand = FALSE ) +
  labs(title = "Assessment Intervals", x = "Frequency of Assessment (Years)", y = "Proportion Healthy")+
  theme(axis.text.x=element_text(size=15), axis.text.y=element_text(size=15), plot.title = element_text(hjust = 0.5, face = "bold", size = 20), axis.title.x = element_text(face = "bold", size = 15), axis.title.y = element_text(face = "bold", size = 15), legend.title.align=0.5, panel.background = element_rect(fill = "transparent",colour = NA), plot.background = element_rect(fill = "transparent",colour = NA), legend.title=element_text(size=15), 
    legend.text=element_text(size=12),legend.key = element_rect(fill = "transparent", colour = "transparent"), legend.background = element_blank(),
    legend.box.background = element_blank()) 

ai_c_graph

# ggsave(ai_c_graph, filename = "ai_c_noclose.png",  bg = "transparent",
#       width = 6, height = 4)
```

## New Updating Data (no closure)  

```{r read-updating, warning=FALSE, message=FALSE}
ai_u <- read_csv(file=file.path(here(), "/analysis/no_closure/all_data/noclose_all_u.csv"))
```

## Wrangle Updating
```{r wrangle}
##Wrangling with the combined data set:
ai_intervals <- c(20,15,10,5,1) #new intervals in correct order

ai_u[is.na(ai_u)] <- "misc" #turn status NA into misc

# Calculate proportions for graphing:
ai_props_u <- ai_u %>% 
  mutate(assess_int = factor(assess, levels = ai_intervals)) %>%
  group_by(assess_int) %>%
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate(simulations = sum(over + good + misc)) %>% 
  mutate(prop_good = good / simulations)
```

## Create Graphing Data - both

```{r wrangle-graph-data, include=FALSE}

##Create the all graph data frame - start with constant and add updating then merge:
graph_c <- data.frame(assessment_interval = ai_props_c$assess_int, response = rep("none", 5),
                      prop_good = ai_props_c$prop_good)
graph_u <- data.frame(assessment_interval = ai_props_u$assess_int, response = rep("ideal", 5),
                      prop_good = ai_props_u$prop_good)
graph_both <- rbind(graph_c, graph_u)

```


## Graph 2: Constant vs. Updating
```{r graph-both}
ai_both <- ggplot(graph_both, aes(x = assessment_interval, y = prop_good, fill = response)) +
  geom_col(position = "dodge", alpha = 0.8) + 
  scale_fill_manual(values = c("#BC6435", "#079EDF"), name = "Climate Response", labels = c("None", "Ideal"))+
  theme_light()+
  coord_cartesian( ylim=c(0,1), expand = FALSE ) +
  labs(title = "Assessment Intervals", x = "Frequency of Assessment (Years)", y = "Proportion Healthy")+
  theme(axis.text.x=element_text(size=15), axis.text.y=element_text(size=15), plot.title = element_text(hjust = 0.5, face = "bold", size = 20), axis.title.x = element_text(face = "bold", size = 15), axis.title.y = element_text(face = "bold", size = 15), legend.title.align=0.5, panel.background = element_rect(fill = "transparent",colour = NA), plot.background = element_rect(fill = "transparent",colour = NA), legend.title=element_text(size=15), 
    legend.text=element_text(size=12),legend.key = element_rect(fill = "transparent", colour = "transparent"), legend.background = element_blank(),
    legend.box.background = element_blank()) 

ai_both

# ggsave(ai_both, filename = "ai_ideal_noclose.png",  bg = "transparent",
#       width = 6, height = 4)
```

## Proxy Data:
```{r proxy-data, warning=FALSE, message=FALSE}
ai_p <- read_csv(file=file.path(here(),"/Results/productivity_proxy/for_publics/new_model/proxy_new_all_publics.csv"))
```


## Wrangle Proxy:
```{r wrangle-proxy}
ai_intervals <- c(20,15,10,5,1) #new intervals in correct order

ai_p[is.na(ai_p)] <- "misc" #turn status NA into misc

# Calculate proportions for graphing:
ai_props_p <- ai_p %>% 
  mutate(assess_int = factor(ai, levels = ai_intervals)) %>%
  filter(ai != 0) %>% 
  group_by(assess_int) %>%
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate(simulations = sum(over + good + misc)) %>% 
  mutate(prop_good = good / simulations)
```


## Graphing Data: 
```{r graph3-data}
##Create the all graph data frame - start with constant and add updating then merge:
graph_c <- data.frame(assessment_interval = ai_props_c$assess_int, response = rep("none", 5),
                      prop_good = ai_props_c$prop_good)
graph_u <- data.frame(assessment_interval = ai_props_u$assess_int, response = rep("ideal", 5),
                      prop_good = ai_props_u$prop_good)
graph_pre <- data.frame(assessment_interval = ai_props_p$assess_int, response = rep("precautionary", 5),
                        prop_good = ai_props_p$prop_good)
graph_both <- rbind(graph_c, graph_u, graph_pre)
```


## Graph 3 - Constant vs. Updating vs. Proxy  
Colors:  
 - For the original no climate response use: "#BC6435"  
 - For the ideal climate response use:  "#079EDF"   
 - For proxy results (precautionary) try: "#B8CE55" (but this might not look great - we aren't sure)  
 
 
```{r graph3-all}

ai_all <- ggplot(graph_both, aes(x = assessment_interval, y = prop_good, fill = response)) +
  geom_col(position = "dodge", alpha = 0.8) + 
  scale_fill_manual(values = c("#BC6435", "#079EDF", "#B8CE55"), name = "Climate Response", labels = c("None", "Ideal", "Precautionary"))+
  theme_light()+
  coord_cartesian( ylim=c(0,1), expand = FALSE ) +
  labs(title = "Assessment Intervals", x = "Frequency of Assessment (Years)", y = "Proportion Healthy")+
  theme(axis.text.x=element_text(size=15), axis.text.y=element_text(size=15), plot.title = element_text(hjust = 0.5, face = "bold", size = 20), axis.title.x = element_text(face = "bold", size = 15), axis.title.y = element_text(face = "bold", size = 15), legend.title.align=0.5, panel.background = element_rect(fill = "transparent",colour = NA), plot.background = element_rect(fill = "transparent",colour = NA), legend.title=element_text(size=15), 
    legend.text=element_text(size=12),legend.key = element_rect(fill = "transparent", colour = "transparent"), legend.background = element_blank(),
    legend.box.background = element_blank()) 

ai_all

```

