---
title: "miderror_runs"
author: "Sara Orofino"
date: "3/11/2020"
output: html_document
---

Check the mid error runs to see if the assessment interval trend reverses when not closing the fishery for being over the limit  

Read in the mid error datasets:  
```{r}
#Assessment interval 1 year:
mid_1_80 <- read_csv(file=file.path(here(),"/Results/no_closure/miderror/miderr_1_80.csv"))
mid_1_85 <- read_csv(file=file.path(here(),"/Results/no_closure/miderror/miderr_1_85.csv"))
mid_1_90 <- read_csv(file=file.path(here(),"/Results/no_closure/miderror/miderr_1_90.csv"))
mid_1_95 <- read_csv(file=file.path(here(),"/Results/no_closure/miderror/miderr_1_95.csv"))

#Assessment interval 5 year:
mid_5_80 <- read_csv(file=file.path(here(),"/Results/no_closure/miderror/miderr_5_80.csv"))
mid_5_85 <- read_csv(file=file.path(here(),"/Results/no_closure/miderror/miderr_5_85.csv"))
mid_5_90 <- read_csv(file=file.path(here(),"/Results/no_closure/miderror/miderr_5_90.csv"))
mid_5_95 <- read_csv(file=file.path(here(),"/Results/no_closure/miderror/miderr_5_95.csv"))

#Assessment interval 10 years:
mid_10_80 <- read_csv(file=file.path(here(),"/Results/no_closure/miderror/miderr_10_80.csv"))
mid_10_85 <- read_csv(file=file.path(here(),"/Results/no_closure/miderror/miderr_10_85.csv"))
mid_10_90 <- read_csv(file=file.path(here(),"/Results/no_closure/miderror/miderr_10_90.csv"))
mid_10_95 <- read_csv(file=file.path(here(),"/Results/no_closure/miderror/miderr_10_95.csv"))

#Assessment interval 15 years:
mid_15_80 <- read_csv(file=file.path(here(),"/Results/no_closure/miderror/miderr_15_80.csv"))
mid_15_85 <- read_csv(file=file.path(here(),"/Results/no_closure/miderror/miderr_15_85.csv"))
mid_15_90 <- read_csv(file=file.path(here(),"/Results/no_closure/miderror/miderr_15_90.csv"))
mid_15_95 <- read_csv(file=file.path(here(),"/Results/no_closure/miderror/miderr_15_95.csv"))

#Assessment interval 20 years:
mid_20_80 <- read_csv(file=file.path(here(),"/Results/no_closure/miderror/miderr_20_80.csv"))
mid_20_85 <- read_csv(file=file.path(here(),"/Results/no_closure/miderror/miderr_20_85.csv"))
mid_20_90 <- read_csv(file=file.path(here(),"/Results/no_closure/miderror/miderr_20_90.csv"))
mid_20_95 <- read_csv(file=file.path(here(),"/Results/no_closure/miderror/miderr_20_95.csv"))
```


For each data set add the status, growth, and assessment interval, filter for year 100  
Combine the different assessment levels for each of the four over_hcrs   
```{r}
#80% cutback runs:
mid1_80 <- mid_1_80 %>%   
  mutate(status = ifelse(b <= 1000, "over", "good")) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  mutate(assess = "1")

mid5_80 <- mid_5_80 %>%   
  mutate(status = ifelse(b <= 1000, "over", "good")) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  mutate(assess = "5")

mid10_80 <- mid_10_80 %>%   
  mutate(status = ifelse(b <= 1000, "over", "good")) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  mutate(assess = "10")

mid15_80 <- mid_15_80 %>%   
  mutate(status = ifelse(b <= 1000, "over", "good")) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100)%>% 
  mutate(assess = "15")

mid20_80 <- mid_20_80 %>%   
  mutate(status = ifelse(b <= 1000, "over", "good")) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  mutate(assess = "20")

miderr_80 <- rbind(mid1_80, mid5_80, mid10_80, mid15_80, mid20_80)

#85% cutback runs:
mid1_85 <- mid_1_85 %>%   
  mutate(status = ifelse(b <= 1000, "over", "good")) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  mutate(assess = "1")

mid5_85 <- mid_5_85 %>%   
  mutate(status = ifelse(b <= 1000, "over", "good")) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  mutate(assess = "5")

mid10_85 <- mid_10_85 %>%   
  mutate(status = ifelse(b <= 1000, "over", "good")) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  mutate(assess = "10")

mid15_85 <- mid_15_85 %>%   
  mutate(status = ifelse(b <= 1000, "over", "good")) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  mutate(assess = "15")

mid20_85 <- mid_20_85 %>%   
  mutate(status = ifelse(b <= 1000, "over", "good")) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  mutate(assess = "20")

miderr_85 <- rbind(mid1_85, mid5_85, mid10_85, mid15_85, mid20_85)

#90% cutback runs:
mid1_90 <- mid_1_90 %>%   
  mutate(status = ifelse(b <= 1000, "over", "good")) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  mutate(assess = "1")

mid5_90 <- mid_5_90 %>%   
  mutate(status = ifelse(b <= 1000, "over", "good")) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  mutate(assess = "5")

mid10_90 <- mid_10_90 %>%   
  mutate(status = ifelse(b <= 1000, "over", "good")) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  mutate(assess = "10")

mid15_90 <- mid_15_90 %>%   
  mutate(status = ifelse(b <= 1000, "over", "good")) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  mutate(assess = "15")

mid20_90 <- mid_20_90 %>%   
  mutate(status = ifelse(b <= 1000, "over", "good")) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  mutate(assess = "20")

miderr_90 <- rbind(mid1_90, mid5_90, mid10_90, mid15_90, mid20_90) 

#95% cutback runs:
mid1_95 <- mid_1_95 %>%   
  mutate(status = ifelse(b <= 1000, "over", "good")) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  mutate(assess = "1")

mid5_95 <- mid_5_95 %>%   
  mutate(status = ifelse(b <= 1000, "over", "good")) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  mutate(assess = "5")

mid10_95 <- mid_10_95 %>%   
  mutate(status = ifelse(b <= 1000, "over", "good")) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  mutate(assess = "10")

mid15_95 <- mid_15_95 %>%   
  mutate(status = ifelse(b <= 1000, "over", "good")) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  mutate(assess = "15")

mid20_95 <- mid_20_95 %>%   
  mutate(status = ifelse(b <= 1000, "over", "good")) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  mutate(assess = "20")

miderr_95 <- rbind(mid1_95, mid5_95, mid10_95, mid15_95, mid20_95)
```

Create the graphing dataframe for each of the four over_hrc levels:  
```{r graph-data}
prop_80 <- miderr_80 %>% 
  group_by(assess, status) %>% 
  tally() %>% 
  rename("count" = n) %>% 
  spread(key = "status", value = "count") %>% 
  mutate(simulations = 4080) %>% 
  mutate(prop_over = over / simulations)

prop_85 <- miderr_85 %>% 
  group_by(assess, status) %>% 
  tally() %>% 
  rename("count" = n) %>% 
  spread(key = "status", value = "count") %>% 
  mutate(simulations = 4080) %>% 
  mutate(prop_over = over / simulations)

prop_90 <- miderr_90 %>% 
  group_by(assess, status) %>% 
  tally() %>% 
  rename("count" = n) %>% 
  spread(key = "status", value = "count") %>% 
  mutate(simulations = 4080) %>% 
  mutate(prop_over = over / simulations)

prop_95 <- miderr_95 %>% 
  group_by(assess, status) %>% 
  tally() %>% 
  rename("count" = n) %>% 
  spread(key = "status", value = "count") %>% 
  mutate(simulations = 4080) %>% 
  mutate(prop_over = over / simulations)

```

Graph for 80% cutback:   
```{r graph}
#Make sure the assessment intervals is a factor for graphing:
prop_80$assess <- as.factor(prop_80$assess)

graph_80 <- ggplot(prop_80, aes(x=assess, y=prop_over)) + 
  geom_col(position = "dodge", alpha = .7, fill = "#079EDF", width = 0.5)  +
  theme_light()+
  coord_cartesian( ylim=c(0,.55), expand = FALSE ) +
  labs(title = "Assessments Intervals", x = "Frequency of Assessment (Years)", y = "Proportion Overfished")+
  theme(axis.text.x=element_text(size=15), axis.text.y=element_text(size=15), plot.title = element_text(hjust = 0.5, face = "bold", size = 20), axis.title.x = element_text(face = "bold", size = 15), axis.title.y = element_text(face = "bold", size = 15),
        panel.background = element_rect(fill = "transparent",colour = NA),
        plot.background = element_rect(fill = "transparent",colour = NA))
graph_80
```

Graph for 95% cutback:   
```{r graph}
#Make sure the assessment intervals is a factor for graphing:
prop_95$assess <- as.factor(prop_95$assess)

graph_95 <- ggplot(prop_95, aes(x=assess, y=prop_over)) + 
  geom_col(position = "dodge", alpha = .7, fill = "#079EDF", width = 0.5)  +
  theme_light()+
  coord_cartesian( ylim=c(0,.55), expand = FALSE ) +
  labs(title = "Assessments Intervals", x = "Frequency of Assessment (Years)", y = "Proportion Overfished")+
  theme(axis.text.x=element_text(size=15), axis.text.y=element_text(size=15), plot.title = element_text(hjust = 0.5, face = "bold", size = 20), axis.title.x = element_text(face = "bold", size = 15), axis.title.y = element_text(face = "bold", size = 15),
        panel.background = element_rect(fill = "transparent",colour = NA),
        plot.background = element_rect(fill = "transparent",colour = NA))
graph_95
```



80% cutback and 95% cutback aren't that different. Seems the amount of the over limit reduction doesn't matter that much.  


Still confused why 1 year isn't better than 20 years. Doing some exploring:  

```{r explore}

#Line plot of biomass over time for the every year assessment at 80% cutback:
plot1_80 <- mid_1_80 %>% 
  filter(b_0 == 1500) %>% 
  filter(r_s < 0) %>%
  filter(r_s > -0.00767) %>% 
  ggplot(aes(x = year, y = b, group = id)) +
  geom_line(aes(color = r_0)) +
  facet_wrap(~hcr) +
  theme_bw() +
  scale_color_continuous(low = "#079EDF", high = "#B8CE55", name = "Growth Rate") +
  labs(title = "Every year with 80% HCR if over limit", y = "Biomass", x = "Year") +
  theme(axis.text.x=element_text(size=10), plot.title = element_text(hjust = 0.5, face = "bold", size = 15), axis.title.x = element_text(face = "bold"), axis.title.y = element_text(face = "bold"))
plot1_80

#Compare to every 20 years at 80% cutback:
plot20_80 <- mid_20_80 %>% 
  filter(b_0 == 1500) %>% 
  filter(r_s < 0) %>%
  filter(r_s > -0.00767) %>% 
  ggplot(aes(x = year, y = b, group = id)) +
  geom_line(aes(color = r_0)) +
  facet_wrap(~hcr) +
  theme_bw() +
  scale_color_continuous(low = "#079EDF", high = "#B8CE55", name = "Growth Rate") +
  labs(title = "Every 20 years with 80% HCR if over limit", y = "Biomass", x = "Year") +
  theme(axis.text.x=element_text(size=10), plot.title = element_text(hjust = 0.5, face = "bold", size = 15), axis.title.x = element_text(face = "bold"), axis.title.y = element_text(face = "bold"))
plot20_80
```

 
Comparing the two graphs of biomass over time for every year and every 20 year we think the results are because in 20 year assessments you have 20 years of the 80% reduction during which your fishery recovers significantly. Whether that happens initially or after the first or second assessment period the fishing pressure is never hard enough to bring those fisheries down to overfished levels.  





