---
title: "assessment_finalviz"
output: html_document
---

#{.tabset}
```{r setup, include=FALSE}

#Packages
library(tidyverse)
library(here)
library(RColorBrewer)

#Data
rep0c <- read_csv(file=file.path(here(),"/Results/assessment_intervals/ai_constantfmsy_0rep_hcr30.csv"))
rep5c <- read_csv(file=file.path(here(),"/Results/assessment_intervals/ai_constantfmsy_5rep_hcr30.csv"))
rep10c <- read_csv(file=file.path(here(),"/Results/assessment_intervals/ai_constantfmsy_10rep_hcr30.csv"))
rep15c <- read_csv(file=file.path(here(),"/Results/assessment_intervals/ai_constantfmsy_15rep_hcr30.csv"))
rep20c <- read_csv(file=file.path(here(),"/Results/assessment_intervals/ai_constantfmsy_20rep_hcr30.csv"))

rep0u <- read_csv(file=file.path(here(),"Results/assessment_intervals/ai_updatingfmsy_0rep_hcr30.csv"))
rep5u <- read_csv(file=file.path(here(),"Results/assessment_intervals/ai_updatingfmsy_5rep_hcr30.csv"))
rep10u <- read_csv(file=file.path(here(),"Results/assessment_intervals/ai_updatingfmsy_10rep_hcr30.csv"))
rep15u <- read_csv(file=file.path(here(),"Results/assessment_intervals/ai_updatingfmsy_15rep_hcr30.csv"))
rep20u <- read_csv(file=file.path(here(),"Results/assessment_intervals/ai_updatingfmsy_20rep_hcr30.csv"))


```


##Constant Fmsy

Create a bar graph of the proportion of bad outcomes (overfished + closed) in year 100 at the different assessment intervals    

Steps:  
  - For each assessment interval mutate a column for over, good, and closed  
  - Filter for year 100  
  - Calculate the proportion of bad outcomes (closed + over)  
  - Create a graphing df of the proportion of bad outcomes for the different assessment intervals  
  
```{r wrangle-assessment-constant, include = FALSE}
##Rep 0:
bad0_c <- rep0c %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  group_by(status) %>% 
  tally() %>% 
  rename("count" = n) %>% 
  spread(key = "status", value = "count") %>% 
  mutate(simulations = sum(closed + good + over)) %>% 
  mutate(prop_bad = sum(closed + over) / simulations)

##Rep 5:
bad5_c <- rep5c %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  group_by(status) %>% 
  tally() %>% 
  rename("count" = n) %>% 
  spread(key = "status", value = "count") %>% 
  mutate(simulations =  sum(closed + good + over + 3)) %>% 
  mutate(prop_bad = sum(closed + over) / simulations)

##Rep10:
bad10_c <- rep10c %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  group_by(status) %>% 
  tally() %>% 
  rename("count" = n) %>% 
  spread(key = "status", value = "count") %>% 
  mutate(simulations = sum(closed + good + over + 1)) %>% 
  mutate(prop_bad = sum(closed + over) / simulations)


##Rep15:
bad15_c <- rep15c %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  group_by(status) %>% 
  tally() %>% 
  rename("count" = n) %>% 
  spread(key = "status", value = "count") %>% 
  mutate(simulations = sum(closed + good + over + 1)) %>% 
  mutate(prop_bad = sum(closed + over) / simulations)


##Rep20:
bad20_c <- rep20c %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  group_by(status) %>% 
  tally() %>% 
  rename("count" = n) %>% 
  spread(key = "status", value = "count") %>% 
  mutate(simulations = sum(closed + good + over + 2)) %>% 
  mutate(prop_bad = sum(closed + over) / simulations)


###Combine for graphing:
intervals <- c(5,10,15,20,"Never") #create the assessment interval column
prop <- c(bad5_c$prop_bad, bad10_c$prop_bad, bad15_c$prop_bad, bad20_c$prop_bad, bad0_c$prop_bad)


graph_c <- data.frame(assessment_intervals = intervals, productivity = rep("Constant", 5), prop_bad = prop)

```


Create the graph with prop_bad on y-axis and assessment intervals on the x-axis  

```{r assessment-constant-graph, echo=FALSE}
#Make sure the assessment intervals is a factor for graphing:
graph_c$assessment_intervals <- as.factor(graph_c$assessment_intervals)

prop_bad_c <- ggplot(graph_df, aes(x=assessment_intervals, y=prop_bad)) + 
  geom_col()
prop_bad_c
```

##Constant vs. Updating Fmsy

Graph proportion of bad outcomes (overfished + closed) for constant vs. updating fmsy at the different assessment intervals  

```{r wrangle-assessment-updating, include=FALSE}
##Rep 0:
bad0_u <- rep0u %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  group_by(status) %>% 
  tally() %>% 
  rename("count" = n) %>% 
  spread(key = "status", value = "count") %>% 
  mutate(simulations = sum(closed + good + over)) %>% 
  mutate(prop_bad = sum(closed + over) / simulations)

##Rep 5:
bad5_u <- rep5u %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  group_by(status) %>% 
  tally() %>% 
  rename("count" = n) %>% 
  spread(key = "status", value = "count") %>% 
  mutate(simulations =  sum(closed + good + 1)) %>% 
  mutate(prop_bad = closed / simulations)

##Rep10:
bad10_u <- rep10u %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  group_by(status) %>% 
  tally() %>% 
  rename("count" = n) %>% 
  spread(key = "status", value = "count") %>% 
  mutate(simulations = sum(closed + good + over + 2)) %>% 
  mutate(prop_bad = sum(closed + over) / simulations)


##Rep15:
bad15_u <- rep15u %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  group_by(status) %>% 
  tally() %>% 
  rename("count" = n) %>% 
  spread(key = "status", value = "count") %>% 
  mutate(simulations = sum(closed + good + 1)) %>% 
  mutate(prop_bad = closed / simulations)


##Rep20:
bad20_u <- rep20u %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(year == 100) %>% 
  group_by(status) %>% 
  tally() %>% 
  rename("count" = n) %>% 
  spread(key = "status", value = "count") %>% 
  mutate(simulations = sum(closed + good + over + 2)) %>% 
  mutate(prop_bad = sum(closed + over) / simulations)


###Combine updating props for graphing:
intervals <- c(5,10,15,20,"Never") #create the assessment interval column
prop_u <- c(bad5_u$prop_bad, bad10_u$prop_bad, bad15_u$prop_bad, bad20_u$prop_bad, bad0_u$prop_bad)


graph_u <- data.frame(assessment_intervals = intervals, productivity = rep("Updating", 5), prop_bad = prop_u)

#Combine constant and updating:
graph_both <- rbind(graph_c, graph_u) %>% 
  mutate(assess_int = factor(assessment_intervals, levels = intervals)) #relevel factors for graphing
```

Combined graph:  
```{r graph-both, echo=FALSE}

prop_bad_both <- ggplot(graph_both, aes(x=assess_int, y = prop_bad, fill = productivity)) + 
  geom_col(position = "dodge") 
prop_bad_both
```

