---
title: "error_finalviz"
output: html_document
---

#{.tabset}
```{r setup, include=FALSE, warning=FALSE, message=FALSE}

#Packages
library(tidyverse)
library(here)
library(RColorBrewer)

#Data
err_rep5u <- read_csv(file=file.path(here(),"/Results/error/error_updating_rep5_hcr30.csv"))
err_rep10u <- read_csv(file=file.path(here(),"/Results/error/error_updating_rep10_hcr30.csv"))
err_rep5c <- read_csv(file=file.path(here(),"/Results/error/error_constant_rep5_hcr30.csv"))
err_rep10c <- read_csv(file=file.path(here(),"/Results/error/error_constant_rep10_hcr30.csv"))


#Comparision of perfect management data
perfect <- read_csv(file=file.path(here(),"/Tests/perfect_management/csv_results/perfect_r0.1.csv"))
perfect_fishe <- read_csv(file=file.path(here(),"/Results/error/perfect_updating_rep5_hcr30.csv"))

```


##Constant Fmsy

Create a bar graph of the proportion of fisheries closed in year 100 on the y-axis for the different levels of error  


Steps:  
  - Create a column to track actions using the following criteria:  
      - If the manager made the correct decision --> correct 
      - If the manager made the wrong decision and should have cutback but increased fishing instead --> cutback  
      - If the manager made the wrong decision and should have closed the fishery but didn't --> should_closed  
      - If the manager made the wrong decision and closed the fishery but shouldn't have --> false_close  
      - If the manager made the wrong decision and cutback but could have increased fishing --> increase
      - If the fishery is closed (no decision was made) --> closed
  - Wrangle data to only include assessment years    
  - Group by actions at different error levels   
  - Calculate the proportion of different outcomes    
```{r wrangle-constant, include=FALSE}

#Add column to track if specific actions resulting from different decisions:  
rep5c_edit <- err_rep5c %>% 
  mutate(action = ifelse(correct_decision == "no" & ratio_cat == 2 & ratio_err_cat == 1, "cutback", 
                          ifelse(correct_decision == "no" & ratio_cat == 3, "should_close", 
                                 ifelse(correct_decision == "no" & ratio_cat == 2 & ratio_err_cat == 3, "false_close",
                                        ifelse(correct_decision == "no" & ratio_cat == 1, "increase",
                                               ifelse(correct_decision == "yes", "correct", "closed")))))) %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast")))
         

#Assessment years:
assess_5 <- seq(5,100,5)

#Group based on action and error:
prop_actions_c <- rep5c_edit %>%
  filter(year == 1 | year %in% assess_5) %>% 
  filter(status != "NA") %>% 
  group_by(error, action) %>% 
  tally() %>% 
  rename("count_5c" = n) %>% 
  spread(key = "action", value = "count_5c") %>% 
  mutate(wrong_decision = sum(cutback + false_close + increase + should_close)) %>% 
  mutate(total_assessments = sum(closed + correct + cutback + false_close + increase + should_close)) %>%
  mutate(prop_correct = correct / total_assessments) %>% 
  mutate(prop_false_close = false_close / total_assessments) %>% 
  mutate(prop_closed = closed / total_assessments)



prop_bad_c <- rep5c_edit %>% 
  filter(year == 1 | year %in% assess_5) %>%
  group_by(error, correct_decision) %>% 
  tally() %>% 
  rename("count_5c" = n) %>% 
  spread(key = "correct_decision", value = "count_5c") %>% 
  mutate(total_decisions = sum(yes + no)) %>% 
  mutate(total_assessments = sum(yes + no + fail)) %>% 
  mutate(prop_wrong = no / total_decisions) %>% 
  mutate(prop_closed = fail / total_assessments)

```


```{r year100, include=FALSE}
##Looking at outcomes only in year 100 
#First find proportion of bad outcomes in year 100 (fisheries closed + overfished)
prop_100_c <- rep5c_edit %>% 
  filter(year == 100) %>% 
  filter(status != "NA") %>% 
  group_by(error, status) %>% 
  tally() %>% 
  rename("count_5c" = n) %>% 
  spread(key = "status", value = "count_5c") %>% 
  mutate(simulations = sum(closed + good + over)) %>% 
  mutate(prop_over = over / simulations) %>% 
  mutate(prop_closed = closed / simulations) %>% 
  mutate(prop_bad = sum(over + closed) / simulations)


```


```{r constant-graphs, echo=FALSE}
#Want to have error as a factor so that the graphs have a discrete x-axis:
prop_100_c$error <- as.factor(prop_100_c$error)


#Graph with prop bad outcomes in year 100 (overfished + closed):
prop_bad100_c <- ggplot(prop_100_c, aes(x = error, y = prop_bad)) +
  geom_col()
prop_bad100_c


#Graph with prop closed in year 100 (out of the 408 simulations for each error bucket how many were closed in year 100) on y axis:
# prop_closed100_c <- ggplot(prop_100_c, aes(x = error, y = prop_closed)) + 
#   geom_col()
# prop_closed100_c
```

##Constant vs. Updating Fmsy

For Test 4 we need to have a bar graph of proportion of bad outcomes for constant vs. updating fmsy   

First, wrangle data using the open, closed, overfished in year 100 and then graph both  

```{r wrangle-updating, include=FALSE}
prop_100_u <- err_rep5u %>% 
  filter(year == 100) %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  filter(status != "NA") %>% 
  group_by(error, status) %>% 
  tally() %>% 
  rename("count_5c" = n) %>% 
  spread(key = "status", value = "count_5c") %>% 
  mutate(simulations = sum(closed + good)) %>% 
  mutate(prop_bad = closed / simulations) 

##Create the graph data frame - start with constant and updating then merge:
graph_c <- data.frame(error = prop_100_c$error, productivity = rep("constant", 3), prop_bad = prop_100_c$prop_bad)
graph_u <- data.frame(error = prop_100_u$error, productivity = rep("updating", 3), prop_bad = prop_100_u$prop_bad)
graph_both <- rbind(graph_c, graph_u)
```

```{r combined-graph, echo=FALSE}
#Want to have error as a factor so that the graphs have a discrete x-axis:
graph_both$error <- as.factor(graph_both$error)

prop_100_both <- ggplot(graph_both, aes(x=error, y = prop_bad, fill = productivity)) + 
  geom_col(position = "dodge") 
prop_100_both
```

