---
title: "discussion_presentation_data_exploration"
author: "Chase Brewster"
date: "1/23/2020"
output: html_document
---
#{.tabset}

##Step 1
This .Rmd holds every combination of expirements we have ran. It has all assessment intervals (0, 20, 15, 10, 5, every year), tested against all errors (.5, .3, .1), and all harvest control rules (.95 - .50), under the constant fmsy scenario.

The resulting dataset - "alldata" - can then be altered independently to create different data explorations and visualizations.

To explore data, follow the steps below:

1. Packages Needed
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
```

##Step 2
2. Read in the csv files, add columns for data exploration grouping, and bind all csv's to the main data set, "alldata"

```{r message = FALSE, warning = FALSE}
low_err <- read_csv(file=file.path(here(),"/Presentation/discussion/decisiontable_lowerr.csv"))
mid_err <- read_csv(file=file.path(here(),"/Presentation/discussion/decisiontable_miderr.csv"))
high_err <- read_csv(file=file.path(here(),"/Presentation/discussion/decisiontable_higherr.csv"))

low_err_10 <- read_csv(file=file.path(here(),"/Presentation/discussion/decisiontable_lowerr_10.csv"))
mid_err_10 <- read_csv(file=file.path(here(),"/Presentation/discussion/decisiontable_miderr_10.csv"))
high_err_10 <- read_csv(file=file.path(here(),"/Presentation/discussion/decisiontable_higherr_10.csv"))

low_err_15 <- read_csv(file=file.path(here(),"/Presentation/discussion/decisiontable_lowerr_15.csv"))
mid_err_15 <- read_csv(file=file.path(here(),"/Presentation/discussion/decisiontable_miderr_15.csv"))
high_err_15 <- read_csv(file=file.path(here(),"/Presentation/discussion/decisiontable_higherr_15.csv"))

low_err_20 <- read_csv(file=file.path(here(),"/Presentation/discussion/decisiontable_lowerr_20.csv"))
mid_err_20 <- read_csv(file=file.path(here(),"/Presentation/discussion/decisiontable_miderr_20.csv"))
high_err_20 <- read_csv(file=file.path(here(),"/Presentation/discussion/decisiontable_higherr_20.csv"))

low_err_0 <- read_csv(file=file.path(here(),"/Presentation/discussion/decisiontable_lowerr_0.csv"))
mid_err_0 <- read_csv(file=file.path(here(),"/Presentation/discussion/decisiontable_miderr_0.csv"))
high_err_0 <- read_csv(file=file.path(here(),"/Presentation/discussion/decisiontable_higherr_0.csv"))

low_err_all <- read_csv(file=file.path(here(),"/Presentation/discussion/decisiontable_lowerr_all.csv"))
mid_err_all <- read_csv(file=file.path(here(),"/Presentation/discussion/decisiontable_miderr_all.csv"))
high_err_all <- read_csv(file=file.path(here(),"/Presentation/discussion/decisiontable_higherr_all.csv"))

low_err_1 <- low_err %>% 
  filter(year == 100) %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  mutate(assess = "5")

mid_err_1 <- mid_err %>% 
  filter(year == 100) %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  mutate(assess = "5")

high_err_1 <- high_err %>% 
  filter(year == 100) %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  mutate(assess = "5")
  
low_err_2 <- low_err_10 %>% 
  filter(year == 100) %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  mutate(assess = "10")

mid_err_2 <- mid_err_10 %>% 
  filter(year == 100) %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  mutate(assess = "10")

high_err_2 <- high_err_10 %>% 
  filter(year == 100) %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  mutate(assess = "10")
  
low_err_3 <- low_err_15 %>% 
  filter(year == 100) %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  mutate(assess = "15")

mid_err_3 <- mid_err_15 %>% 
  filter(year == 100) %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  mutate(assess = "15")

high_err_3 <- high_err_15 %>% 
  filter(year == 100) %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  mutate(assess = "15")

low_err_4 <- low_err_20 %>% 
  filter(year == 100) %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  mutate(assess = "20")

mid_err_4 <- mid_err_20 %>% 
  filter(year == 100) %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  mutate(assess = "20")

high_err_4 <- high_err_20 %>% 
  filter(year == 100) %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  mutate(assess = "20")

low_err_5 <- low_err_0 %>% 
  filter(year == 100) %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  mutate(assess = "0")

mid_err_5 <- mid_err_0 %>% 
  filter(year == 100) %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  mutate(assess = "0")

high_err_5 <- high_err_0 %>% 
  filter(year == 100) %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  mutate(assess = "0")

low_err_6 <- low_err_all %>% 
  filter(year == 100) %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  mutate(assess = "all")

mid_err_6 <- mid_err_all %>% 
  filter(year == 100) %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  mutate(assess = "all")

high_err_6 <- high_err_all %>% 
  filter(year == 100) %>% 
  mutate(status = ifelse(f_ratio == 0, "closed", ifelse(b <= 1000, "over", "good"))) %>% 
  mutate(growth = ifelse(r_0 <= .3, "slow", ifelse(r_0 > .3 & r_0 <= .5, "medium", "fast"))) %>% 
  mutate(assess = "all")


alldata <- rbind(low_err_1, mid_err_1, high_err_1, low_err_2, mid_err_2, high_err_2, low_err_3, mid_err_3, high_err_3, low_err_4, mid_err_4, high_err_4, low_err_5, mid_err_5, high_err_5, low_err_6, mid_err_6, high_err_6)

#Write as CSV:
#write.csv(alldata, file=file.path(here(),"/Presentation/discussion/alldata.csv"),
#           row.names = FALSE)

```


3. From here, use the "alldata" dataset to explore different combinations. Always create a new dataframe for the specific exploration when using "alldata" to avoid writing over the main dataset.

We will have to recategorize some variables as factors to properly group and graph.

```{r read-alldata, warning = FALSE, message = FALSE}
alldata <- read_csv("alldata.csv")

#Change the NA to "all"
alldata[is.na(alldata)] <- "all" #turn NAs to all
```


##Assessment + Error

Assessment Intervals & Error  

```{r assess-error-wrangle, include = FALSE, message = FALSE, warning = FALSE}

###Moderate climate change
#All biomasses, separated by growth rates:
ae_mod_growth <- alldata %>% 
  group_by(error, growth, assess) %>%
  filter(r_s <= 0) %>%
  filter(r_s >= -0.00767) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (closed + over)/(good + over + closed)) %>% 
  mutate(prop_over = over / (good + over + closed)) %>% 
  mutate(prop_closed = (closed)/(good + over + closed))

#Factors:
ae_mod_growth$error <- as.factor(ae_mod_growth$error)
ae_mod_growth$assess <- as.factor(ae_mod_growth$assess)

#All biomasses, separated by initial biomass:
ae_mod_b0 <- alldata %>% 
  group_by(error, b_0, assess) %>%
  filter(r_s <= 0) %>%
  filter(r_s >= -0.00767) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (closed + over)/(good + over + closed)) %>% 
  mutate(prop_closed = (closed)/(good + over + closed))

#Factors:
ae_mod_b0$error <- as.factor(ae_mod_b0$error)
ae_mod_b0$assess <- as.factor(ae_mod_b0$assess)

#All biomasses, separated by HCRs:
ae_mod_hcr <- alldata %>% 
  group_by(error, hcr, assess) %>%
  filter(r_s <= 0) %>%
  filter(r_s >= -0.00767) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (closed + over)/(good + over + closed)) %>% 
  mutate(prop_closed = (closed)/(good + over + closed))

#Factors:
ae_mod_hcr$error <- as.factor(ae_mod_hcr$error)
ae_mod_hcr$assess <- as.factor(ae_mod_hcr$assess)


##Severe climate change
#All biomasses, separated by growth rates:  
ae_severe_growth <- alldata %>% 
  group_by(error, growth, assess) %>%
  filter(r_s < -0.00767) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (closed + over)/(good + over + closed)) %>%
  mutate(prop_over = over / (good + over + closed)) %>% 
  mutate(prop_closed = (closed)/(good + over + closed))

#Factors:
ae_severe_growth$error <- as.factor(ae_severe_growth$error)
ae_severe_growth$assess <- as.factor(ae_severe_growth$assess)

#All biomasses, separated by initial biomass:  
ae_severe_b0 <- alldata %>% 
  group_by(error, b_0, assess) %>%
  filter(r_s < -0.00767) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (closed + over)/(good + over + closed)) %>%
  mutate(prop_over = over / (good + over + closed)) %>% 
  mutate(prop_closed = (closed)/(good + over + closed))

#Factors: 
ae_severe_b0$error <- as.factor(ae_severe_b0$error)
ae_severe_b0$assess <- as.factor(ae_severe_b0$assess)

#All biomasses, separated by HCR:  
ae_severe_hcr <- alldata %>% 
  group_by(error, hcr, assess) %>%
  filter(r_s < -0.00767) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (closed + over)/(good + over + closed)) %>%
  mutate(prop_over = over / (good + over + closed)) %>% 
  mutate(prop_closed = (closed)/(good + over + closed))

#Factors: 
ae_severe_hcr$error <- as.factor(ae_severe_hcr$error)
ae_severe_hcr$assess <- as.factor(ae_severe_hcr$assess)
```

Graphs:   

Moderate climate change - facet wrap by growth rates:   
```{r echo = FALSE, message = FALSE}
ae_mod_growth_graph <- ggplot(ae_mod_growth, aes(x = assess, y = prop_bad, fill = error))  + 
  geom_col(position = "dodge") + 
  facet_wrap(~growth)

ae_mod_growth_graph
```


Severe climate change - facet wrap by growth rates:  
```{r echo = FALSE, message = FALSE}
ae_severe_growth_graph <- ggplot(ae_severe_growth, aes(x = assess, y = prop_bad, fill = error))  + 
  geom_col(position = "dodge") + 
  facet_wrap(~growth)

ae_severe_growth_graph
```


Moderate climate change - facet wrap by initial biomass:  
```{r echo = FALSE, message = FALSE}
ae_mod_b0_graph <- ggplot(ae_mod_b0, aes(x = assess, y = prop_bad, fill = error))  + 
  geom_col(position = "dodge") + 
  facet_wrap(~b_0)

ae_mod_b0_graph
```


Severe climate change - facet wrap by initial biomass:  
```{r echo = FALSE, message = FALSE, warning = FALSE}
ae_severe_b0_graph <- ggplot(ae_severe_b0, aes(x = assess, y = prop_bad, fill = error))  + 
  geom_col(position = "dodge") + 
  facet_wrap(~b_0)

ae_severe_b0_graph
```


Moderate climate change - facet wrap by HCR
```{r echo = FALSE, message = FALSE}
ae_mod_hcr_graph <- ggplot(ae_mod_hcr, aes(x = assess, y = prop_bad, fill = error))  + 
  geom_col(position = "dodge") + 
  facet_wrap(~hcr)

ae_mod_hcr_graph
```


Severe climate change - facet wrap by HCR
```{r echo = FALSE, message = FALSE, warning = FALSE}
ae_severe_hcr_graph <- ggplot(ae_severe_hcr, aes(x = assess, y = prop_bad, fill = error))  + 
  geom_col(position = "dodge") + 
  facet_wrap(~hcr)

ae_severe_hcr_graph
```


##Error + HCRs

Error & Harvest Control Rules  

```{r error-hcr-wrangle, include = FALSE, message = FALSE, warning = FALSE}

###Moderate climate change
#All biomasses, separated by growth rates:
ehcr_mod_growth <- alldata %>% 
  group_by(error, growth, hcr) %>%
  filter(r_s <= 0) %>%
  filter(r_s >= -0.00767) %>% 
  filter(hcr == 0.9 | hcr == 0.8 | hcr == 0.7 | hcr == 0.6 | hcr == 0.5) %>%
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (closed + over)/(good + over + closed)) %>% 
  mutate(prop_closed = (closed)/(good + over + closed)) %>% 
  mutate(prop_over = over / (good + over + closed))

#Factors:
ehcr_mod_growth$error <- as.factor(ehcr_mod_growth$error)
ehcr_mod_growth$hcr <- as.factor(ehcr_mod_growth$hcr)

#All biomasses, separated by initial biomass:
ehcr_mod_b0 <- alldata %>% 
  group_by(error, b_0, hcr) %>%
  filter(r_s <= 0) %>%
  filter(r_s >= -0.00767) %>% 
  filter(hcr == 0.9 | hcr == 0.8 | hcr == 0.7 | hcr == 0.6 | hcr == 0.5) %>%
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (closed + over)/(good + over + closed)) %>% 
  mutate(prop_closed = (closed)/(good + over + closed)) %>% 
  mutate(prop_over = over / (good + over + closed))

#Factors:
ehcr_mod_b0$error <- as.factor(ehcr_mod_b0$error)
ehcr_mod_b0$hcr <- as.factor(ehcr_mod_b0$hcr)

#All biomasses, separated by assessment interval:
ehcr_mod_ai <- alldata %>% 
  group_by(error, assess, hcr) %>%
  filter(r_s <= 0) %>%
  filter(r_s >= -0.00767) %>% 
  filter(hcr == 0.9 | hcr == 0.8 | hcr == 0.7 | hcr == 0.6 | hcr == 0.5) %>%
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (closed + over)/(good + over + closed)) %>% 
  mutate(prop_closed = (closed)/(good + over + closed)) %>% 
  mutate(prop_over = over / (good + over + closed))

#Factors:
ehcr_mod_ai$error <- as.factor(ehcr_mod_ai$error)
ehcr_mod_ai$hcr <- as.factor(ehcr_mod_ai$hcr)
ehcr_mod_ai$assess <- as.factor(ehcr_mod_ai$assess)

##Severe climate change
#All biomasses, separated by growth rates:  
ehcr_severe_growth <- alldata %>% 
  group_by(error, growth, hcr) %>%
  filter(r_s < -0.00767) %>% 
  filter(hcr == 0.9 | hcr == 0.8 | hcr == 0.7 | hcr == 0.6 | hcr == 0.5) %>%
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (closed + over)/(good + over + closed)) %>%
  mutate(prop_over = over / (good + over + closed)) %>% 
  mutate(prop_closed = (closed)/(good + over + closed)) 

#Factors:
ehcr_severe_growth$error <- as.factor(ehcr_severe_growth$error)
ehcr_severe_growth$hcr <- as.factor(ehcr_severe_growth$hcr)

#All biomasses, separated by initial biomass:  
ehcr_severe_b0 <- alldata %>% 
  group_by(error, b_0, hcr) %>%
  filter(r_s < -0.00767) %>% 
  filter(hcr == 0.9 | hcr == 0.8 | hcr == 0.7 | hcr == 0.6 | hcr == 0.5) %>%
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (closed + over)/(good + over + closed)) %>%
  mutate(prop_over = over / (good + over + closed)) %>% 
  mutate(prop_closed = (closed)/(good + over + closed))

#Factors: 
ehcr_severe_b0$error <- as.factor(ehcr_severe_b0$error)
ehcr_severe_b0$hcr <- as.factor(ehcr_severe_b0$hcr)

#All biomasses, separated by assessment intervals:  
ehcr_severe_ai <- alldata %>% 
  group_by(error, assess, hcr) %>%
  filter(r_s < -0.00767) %>% 
  filter(hcr == 0.9 | hcr == 0.8 | hcr == 0.7 | hcr == 0.6 | hcr == 0.5) %>%
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (closed + over)/(good + over + closed)) %>%
  mutate(prop_over = over / (good + over + closed)) %>% 
  mutate(prop_closed = (closed)/(good + over + closed))

#Factors: 
ehcr_severe_ai$error <- as.factor(ehcr_severe_ai$error)
ehcr_severe_ai$hcr <- as.factor(ehcr_severe_ai$hcr)
ehcr_severe_ai$assess <- as.factor(ehcr_severe_ai$assess)
```


Graphs:    
Moderate climate change - facet wrap by growth rates:   
```{r echo = FALSE, message = FALSE}
ehcr_mod_growth_graph <- ggplot(ehcr_mod_growth, aes(x = hcr, y = prop_bad, fill = error))  + 
  geom_col(position = "dodge") + 
  facet_wrap(~growth)

ehcr_mod_growth_graph
```


Severe climate change - facet wrap by growth rates:  
```{r echo = FALSE, message = FALSE}
ehcr_severe_growth_graph <- ggplot(ehcr_severe_growth, aes(x = hcr, y = prop_bad, fill = error))  + 
  geom_col(position = "dodge") + 
  facet_wrap(~growth)

ehcr_severe_growth_graph
```



Moderate climate change - facet wrap by initial biomass:  
```{r echo = FALSE, message = FALSE}
ehcr_mod_b0_graph <- ggplot(ehcr_mod_b0, aes(x = hcr, y = prop_bad, fill = error))  + 
  geom_col(position = "dodge") + 
  facet_wrap(~b_0)

ehcr_mod_b0_graph
```


Severe climate change - facet wrap by initial biomass:  
```{r echo = FALSE, message = FALSE, warning = FALSE}
ehcr_severe_b0_graph <- ggplot(ehcr_severe_b0, aes(x = hcr, y = prop_bad, fill = error))  + 
  geom_col(position = "dodge") + 
  facet_wrap(~b_0)

ehcr_severe_b0_graph
```


Moderate climate change - facet wrap by assessment interval:  
```{r echo = FALSE, message = FALSE}
ehcr_mod_ai_graph <- ggplot(ehcr_mod_ai, aes(x = hcr, y = prop_bad, fill = error))  + 
  geom_col(position = "dodge") + 
  facet_wrap(~assess)

ehcr_mod_ai_graph
```


Severe climate change - facet wrap by assessment interval:  
```{r echo = FALSE, message = FALSE, warning = FALSE}
ehcr_severe_ai_graph <- ggplot(ehcr_severe_ai, aes(x = hcr, y = prop_bad, fill = error))  + 
  geom_col(position = "dodge") + 
  facet_wrap(~assess)

ehcr_severe_ai_graph
```


##HCRs + Assess

Harvest Control Rules & Assessment Intervals  


```{r hcr-assess-wrangle, include = FALSE, message = FALSE, warning = FALSE}

###Moderate climate change
#All biomasses, separated by growth rates:
ahcr_mod_growth <- alldata %>% 
  group_by(assess, growth, hcr) %>%
  filter(r_s <= 0) %>%
  filter(r_s >= -0.00767) %>% 
  filter(hcr == 0.9 | hcr == 0.8 | hcr == 0.7 | hcr == 0.6 | hcr == 0.5) %>%
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (closed + over)/(good + over + closed)) %>% 
  mutate(prop_closed = (closed)/(good + over + closed)) %>% 
  mutate(prop_over = over / (good + over + closed))

#Factors:
ahcr_mod_growth$assess <- as.factor(ahcr_mod_growth$assess)
ahcr_mod_growth$hcr <- as.factor(ahcr_mod_growth$hcr)

#All biomasses, separated by initial biomass:
ahcr_mod_b0 <- alldata %>% 
  group_by(assess, b_0, hcr) %>%
  filter(r_s <= 0) %>%
  filter(r_s >= -0.00767) %>% 
  filter(hcr == 0.9 | hcr == 0.8 | hcr == 0.7 | hcr == 0.6 | hcr == 0.5) %>%
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (closed + over)/(good + over + closed)) %>% 
  mutate(prop_closed = (closed)/(good + over + closed)) %>% 
  mutate(prop_over = over / (good + over + closed))

#Factors:
ahcr_mod_b0$assess <- as.factor(ahcr_mod_b0$assess)
ahcr_mod_b0$hcr <- as.factor(ahcr_mod_b0$hcr)

#All biomasses, separated by error:
ahcr_mod_err <- alldata %>% 
  group_by(assess, error, hcr) %>%
  filter(r_s <= 0) %>%
  filter(r_s >= -0.00767) %>% 
  filter(hcr == 0.9 | hcr == 0.8 | hcr == 0.7 | hcr == 0.6 | hcr == 0.5) %>%
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (closed + over)/(good + over + closed)) %>% 
  mutate(prop_closed = (closed)/(good + over + closed)) %>% 
  mutate(prop_over = over / (good + over + closed))

#Factors:
ahcr_mod_err$assess <- as.factor(ahcr_mod_err$assess)
ahcr_mod_err$hcr <- as.factor(ahcr_mod_err$hcr)
ahcr_mod_err$error <- as.factor(ahcr_mod_err$error)


##Severe climate change
#All biomasses, separated by growth rates:  
ahcr_severe_growth <- alldata %>% 
  group_by(assess, growth, hcr) %>%
  filter(r_s < -0.00767) %>% 
  filter(hcr == 0.9 | hcr == 0.8 | hcr == 0.7 | hcr == 0.6 | hcr == 0.5) %>%
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (closed + over)/(good + over + closed)) %>%
  mutate(prop_over = over / (good + over + closed)) %>% 
  mutate(prop_closed = (closed)/(good + over + closed)) 

#Factors:
ahcr_severe_growth$assess <- as.factor(ahcr_severe_growth$assess)
ahcr_severe_growth$hcr <- as.factor(ahcr_severe_growth$hcr)

#All biomasses, separated by initial biomass:  
ahcr_severe_b0 <- alldata %>% 
  group_by(assess, b_0, hcr) %>%
  filter(r_s < -0.00767) %>% 
  filter(hcr == 0.9 | hcr == 0.8 | hcr == 0.7 | hcr == 0.6 | hcr == 0.5) %>%
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (closed + over)/(good + over + closed)) %>%
  mutate(prop_over = over / (good + over + closed)) %>% 
  mutate(prop_closed = (closed)/(good + over + closed))

#Factors: 
ahcr_severe_b0$assess <- as.factor(ahcr_severe_b0$assess)
ahcr_severe_b0$hcr <- as.factor(ahcr_severe_b0$hcr)

#All biomasses, separated by error:  
ahcr_severe_err <- alldata %>% 
  group_by(assess, error, hcr) %>%
  filter(r_s < -0.00767) %>% 
  filter(hcr == 0.9 | hcr == 0.8 | hcr == 0.7 | hcr == 0.6 | hcr == 0.5) %>%
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (closed + over)/(good + over + closed)) %>%
  mutate(prop_over = over / (good + over + closed)) %>% 
  mutate(prop_closed = (closed)/(good + over + closed))

#Factors: 
ahcr_severe_err$assess <- as.factor(ahcr_severe_err$assess)
ahcr_severe_err$hcr <- as.factor(ahcr_severe_err$hcr)
ahcr_severe_err$error <- as.factor(ahcr_severe_err$error)
```


Graphs:   

Moderate climate change - facet wrap by growth rates:  
```{r echo = FALSE, message = FALSE}
#fill by HCR:
ahcr_mod_growth_graph <- ggplot(ahcr_mod_growth, aes(x = assess, y = prop_bad, fill = hcr))  + 
  geom_col(position = "dodge") + 
  facet_wrap(~growth)

ahcr_mod_growth_graph

#Opposite - fill by assessment interval:
ahcr_mod_growth_graph2 <- ggplot(ahcr_mod_growth, aes(x = hcr, y = prop_bad, fill = assess))  + 
  geom_col(position = "dodge") + 
  facet_wrap(~growth)

ahcr_mod_growth_graph2
```



Severe climate change - facet wrap by growth rates:    
```{r echo = FALSE, message = FALSE}
#fill by HCR:
ahcr_severe_growth_graph <- ggplot(ahcr_severe_growth, aes(x = assess, y = prop_bad, fill = hcr))  + 
  geom_col(position = "dodge") + 
  facet_wrap(~growth)

ahcr_severe_growth_graph

#Opposite - fill by assessment interval:
ahcr_severe_growth_graph2 <- ggplot(ahcr_severe_growth, aes(x = hcr, y = prop_bad, fill = assess))  + 
  geom_col(position = "dodge") + 
  facet_wrap(~growth)

ahcr_severe_growth_graph2
```



Moderate climate change - facet wrap by initial biomass:  
```{r echo = FALSE, message = FALSE}
#fill by HCR:
ahcr_mod_b0_graph <- ggplot(ahcr_mod_b0, aes(x = assess, y = prop_bad, fill = hcr))  + 
  geom_col(position = "dodge") + 
  facet_wrap(~b_0)

ahcr_mod_b0_graph

#Opposite - fill by assessment interval:
ahcr_mod_b0_graph2 <- ggplot(ahcr_mod_b0, aes(x = hcr, y = prop_bad, fill = assess))  + 
  geom_col(position = "dodge") + 
  facet_wrap(~b_0)

ahcr_mod_b0_graph2
```



Severe climate change facet wrap by initial biomass:  
```{r echo = FALSE, message = FALSE}
#fill by HCR:
ahcr_severe_b0_graph <- ggplot(ahcr_severe_b0, aes(x = assess, y = prop_bad, fill = hcr))  + 
  geom_col(position = "dodge") + 
  facet_wrap(~b_0)

ahcr_severe_b0_graph

#Opposite - fill by assessment interval:
ahcr_severe_b0_graph2 <- ggplot(ahcr_severe_b0, aes(x = hcr, y = prop_bad, fill = assess))  + 
  geom_col(position = "dodge") + 
  facet_wrap(~b_0)

ahcr_severe_b0_graph2
```


Moderate climate change - facet wrap by error:  
```{r echo = FALSE, message = FALSE}
#fill by HCR:
ahcr_mod_err_graph <- ggplot(ahcr_mod_err, aes(x = assess, y = prop_bad, fill = hcr))  + 
  geom_col(position = "dodge") + 
  facet_wrap(~error)

ahcr_mod_err_graph

#Opposite - fill by assessment interval:
ahcr_mod_err_graph2 <- ggplot(ahcr_mod_err, aes(x = hcr, y = prop_bad, fill = assess))  + 
  geom_col(position = "dodge") + 
  facet_wrap(~error)

ahcr_mod_err_graph2
```


Severe climate change - facet wrap by error:  
```{r echo = FALSE, message = FALSE}
#fill by HCR:
ahcr_severe_err_graph <- ggplot(ahcr_severe_err, aes(x = assess, y = prop_bad, fill = hcr))  + 
  geom_col(position = "dodge") + 
  facet_wrap(~error)

ahcr_severe_err_graph

#Opposite - fill by assessment interval:
ahcr_severe_err_graph2 <- ggplot(ahcr_severe_err, aes(x = hcr, y = prop_bad, fill = assess))  + 
  geom_col(position = "dodge") + 
  facet_wrap(~error)

ahcr_severe_err_graph2
```


##Gracie Exploration 
```{r}


gracie_alldata <- alldata %>% 
  group_by(assess, growth, hcr, error) %>%
  filter(r_s <= 0) %>%
  filter(r_s >= -0.00767) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (closed + over)/(good + over + closed)) %>% 
  mutate(prop_closed = (closed)/(good + over + closed)) %>% 
  mutate(prop_over = (over)/(good + over))


gracie_alldata$assess <- as.numeric(gracie_alldata$assess)
gracie_alldata$hcr <- as.numeric(gracie_alldata$hcr)

bin_plot <- ggplot(gracie_alldata, aes(x=hcr, y = prop_bad))+
  geom_bin2d()
bin_plot

#sort of cool but not that helpful 
density_plot <- ggplot(gracie_alldata, aes(y = prop_bad, x = hcr)) +
  geom_point() +
  stat_density_2d(aes(fill = ..level..), geom="polygon") 

density_plot

```

##Some Thoughts

- Generally, severe climate change is really bad on all fronts. I think we should stick with moderate climate change for the trade-off discussion in the presentation, and probably the report too. Severe climate may have to be an entirely different discussion itself. Maybe when we come up with a proxy for tracking Fmsy that might be a better answer for the severe situations.

Starting at 0.5 error, with no management (no reassess period, no hcr) - adding reassessment intervals doesn't seem to make much of a difference at this error level. It would take a crazy hcr to get to a decent proportion of bad outcomes. So the most impactful move from here I think would be to get to 0.3 error.

Once at 0.3 error, then there starts being some comparable trade offs between upping the assessment intervals vs. hcrs. vs getting down to 0.1 error. A 0.7 hcr at 0.3 error seems like the point thats better than a 0.5 error with a 0.5 hcr. The assessment intervals get a little bit better but not super significant relatively.

Getting down to 0.1 error can be better than the rest even with a 0.9 hcr. But closing that .3 - .1 gap may be harder to do than the .5 - .3 gap. A 0.7 hcr might be easier to put in rather than getting error down  to 0.1 but  who knows.

```{r}
alldata_counts <- alldata %>% 
  group_by(error, hcr) %>%
  filter(assess != "0") %>% 
  filter(growth == "slow") %>% 
  filter(b_0 == 1500) %>% 
  filter(r_s <= 0) %>%
  filter(r_s >= -0.00767) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (closed + over)/(good + over + closed)) %>% 
  mutate(prop_over = over / (good + over + closed)) %>% 
  mutate(prop_closed = (closed)/(good + over + closed))
```

