---
title: "discussion_graph_filtered"
output: html_document
---

#{.tabset}

##Setup

```{r include = FALSE, warning=FALSE, message = FALSE}
library(tidyverse)

alldata <- read_csv("alldata.csv")

```


##Data Wrangling

After exploration we are highlighting the following scenarios, which are further filtered from the other graph we are showing:    

Initial conditions:  
climate = Moderate (-0.00767 - 0)  
B0 = 1500  
Growth = slow  



Combinations:  

1. Error = 0.3 and HCR = 0.65 and Assess = 10  
2. Error = 0.3 and HCR = 0.7 and Assess = 5    
3. Error = 0.1 and HCR = 0.9 and Assess = 20  
4. Error = 0.1 and HCR = 0.95 and Assess = 5  

```{r include = FALSE}

#Create the baseline conditions df:
baseline <- alldata %>% 
  filter(r_s < 0) %>% 
  filter(r_s >= -0.00767) %>% 
  filter(year == 100) %>% 
  filter(growth == "slow") %>% 
  filter(b_0 == 1500)


#Scenario 1:
scen1 <- baseline %>% 
  filter(error == 0.3) %>% 
  filter(hcr == 0.65) %>% 
  filter(assess == "10") %>% 
  group_by(error, hcr) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (closed)/(good + closed)) %>% 
  mutate(prop_closed = (closed)/(good + closed)) %>% 
  mutate(prop_over = 0) %>% 
  mutate(scenario = "1")

#Scenario 2:
scen2 <- baseline %>% 
  filter(error == 0.3) %>% 
  filter(hcr == 0.7) %>% 
  filter(assess == "5") %>% 
  group_by(error, hcr) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (closed)/(good + closed)) %>% 
  mutate(prop_closed = (closed)/(good + closed)) %>% 
  mutate(prop_over = 0) %>% 
  mutate(scenario = "2")

#Scenario 3:
scen3 <- baseline %>% 
  filter(error == 0.1) %>% 
  filter(hcr == 0.9) %>% 
  filter(assess == "20") %>% 
  group_by(error, hcr) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (over)/(good + over)) %>% 
  mutate(prop_closed = 0) %>% 
  mutate(prop_over = over / (good + over)) %>% 
  mutate(scenario = "3")

#Scenario 4:
scen4 <- baseline %>% 
  filter(error == 0.1) %>% 
  filter(hcr == 0.95) %>% 
  filter(assess == "5") %>% 
  group_by(error, hcr) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (closed)/(good + closed)) %>% 
  mutate(prop_closed = (closed)/(good + closed)) %>% 
  mutate(prop_over = 0) %>% 
  mutate(scenario = "4")

#Bind scenarios for graphing:
scen_combined <- rbind(scen1, scen2, scen3, scen4)
scen_combined[is.na(scen_combined)] <- 0 #change NA to 0 (for those that didn't have any overfished)

#Stacked graph dataframe: 
numbers <- seq(1,4,1)
type <- c("over", "over", "over", "over", "closed", "closed", "closed", "closed")
prop <- c(scen_combined$prop_over, scen_combined$prop_closed)

scen_stacked <- data.frame(scenario = rep(numbers, 2), type = type, prop = prop)
```

##Graphs

Graph of just scenarios and proportion of bad outcomes:  
```{r echo=FALSE}

scen_graph <- ggplot(scen_combined, aes(x = scenario, y = prop_bad)) + 
  geom_col(aes(fill = type), alpha = 0.7, width = .6, fill = "#079EDF")+
  theme_light()+
  coord_cartesian( ylim=c(0,.25), expand = FALSE ) +
  labs(title = "Trade-Offs", subtitle = "A slow-growing species with low initial biomass", x = "Scenario", y = "Proportion of Failures")+
  scale_x_discrete(labels=c("1" = "Error: 30%\nHCR: 35%\nYears: 10", "2" = "Error: 30%\nHCR: 30%\nYears: 5","3" = "Error: 10%\nHCR: 10%\nYears: 20", "4" = "Error: 10%\nHCR: 5%\nYears: 5")) +
  theme(axis.text.x=element_text(size=15), axis.text.y=element_text(size=15), plot.title = element_text(hjust = 0.5, face = "bold", size = 20), plot.subtitle = element_text(hjust = 0.5, size = 17, face="italic"), axis.title.x = element_text(face = "bold", size = 15, vjust = -.5), axis.title.y = element_text(face = "bold", size = 15), legend.title.align=0.5, panel.background = element_rect(fill = "transparent",colour = NA), plot.background = element_rect(fill = "transparent",colour = NA), legend.title=element_text(size=15), 
    legend.text=element_text(size=12),legend.key = element_rect(fill = "transparent", colour = "transparent"), legend.background = element_blank(),
    legend.box.background = element_blank())

scen_graph

ggsave(scen_graph, filename = "scen_specific.png",  bg = "transparent")

#climate = Moderate (-0.00767 - 0)  
#B0 = 1500  
#Growth = slow  

#1. Error = 0.3 and HCR = 0.65 and Assess = 10  
#2. Error = 0.3 and HCR = 0.7 and Assess = 5    
#3. Error = 0.1 and HCR = 0.9 and Assess = 20  
#4. Error = 0.1 and HCR = 0.95 and Assess = 5  
```

Graph of over/closed proportions:  

```{r echo = FALSE}

scen_stacked_graph <- ggplot(scen_stacked, aes(x = scenario, y = prop, fill = type)) +
  geom_col()

scen_stacked_graph
```

