---
title: "flowchart_data"
author: "Sara Orofino"
date: "1/31/2020"
output: html_document
---

##Setup
```{r}
library(tidyverse)
library(here)

alldata <- read_csv("alldata_combined.csv")
```

##Flowchart Calculations

Calculations to support the flow chart for the discussion.   

Start with the baseline proportion of bad outcomes for a fishery that is slow growing (growth = slow), depleted (b_0 = 1500), with no management (never reassess), no data (error = 0.5), in moderate negative climate change (-0.00767 - 0).

```{r}
#Create the baseline that holds for the whole simulation (growth, b_0, and climate change)
baseline <- alldata %>% 
  filter(b_0 == 1500) %>% 
  filter(growth == "slow") %>%
  filter(r_s < 0) %>% 
  filter(r_s >= -0.00767)

initial <- baseline %>% 
  filter(assess == 0) %>% 
  filter(error == 0.5) %>% 
  group_by(hcr) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (over)/(good + over)) 

#Probably wouldn't be any HCRs if there was no management so just use the prop_bad from 5%
initial_prop <- 0.75
```


Institute a 5% HCR and reassess every 20 years  
```{r}
step1 <- baseline %>% 
  filter(assess == 20) %>% 
  filter(error == 0.5) %>% 
  filter(hcr == 0.95) %>% 
  group_by(hcr) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate(prop_bad = (over + closed)/(good + over + closed)) 
  
```


Then you have some options:  

- Reduce error to 0.3 (still assess every 20 years with 5% HCR)  
- Increase cutback to 15% (still have 0.5 error and 20 year assessment)  
- Increase frequency of assessment to 10 years (still have 0.5 error and 5% HCR)  

```{r}
#Step2 - get more data:
err2 <- baseline %>%
  filter(assess == 20) %>% 
  filter(error == 0.3) %>% 
  filter(hcr == 0.95) %>% 
  group_by(hcr) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate(prop_bad = (over + closed)/(good + over + closed))   

#Step2 - increase cutback:
hcr2 <- baseline %>%
  filter(assess == 20) %>% 
  filter(error == 0.5) %>% 
  filter(hcr == 0.85) %>%
  group_by(hcr) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate(prop_bad = (over + closed)/(good + over + closed))

#Step2 - increase frequency:  
assess2 <- baseline %>%
  filter(assess == 10) %>% 
  filter(error == 0.5) %>% 
  filter(hcr == 0.95) %>% 
  group_by(hcr) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate(prop_bad = (over + closed)/(over + closed))  #no good, only closed and over...
```

This shows that increasing the cutback is the best option. From there -   

More options: 
- Collect more data to get to 0.3 (still assess every 20 years with 15% HCR)
- Increase cutback to 20% (still have 0.5 error and 20 year assessment)  
- Reassess more to 10 years (still have 0.5 error and 15% HCR)  

```{r}
#Step3 - more data:
err3 <- baseline %>%
  filter(assess == 20) %>% 
  filter(error == 0.3) %>% 
  filter(hcr == 0.85) %>% 
  group_by(hcr) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate(prop_bad = (closed + over) / (closed + over + good))

#Step3 - increase cutback:
hcr3 <- baseline %>%
  filter(assess == 20) %>% 
  filter(error == 0.5) %>% 
  filter(hcr == 0.80) %>%
  group_by(hcr) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate(prop_bad = (closed)/(good + closed))

#Step3 - increase frequency:
assess3 <- baseline %>%
  filter(assess == 10) %>% 
  filter(error == 0.5) %>% 
  filter(hcr == 0.85) %>% 
  group_by(hcr) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate(prop_bad = (closed)/(good + closed)) 
```

This shows that decreasing error is the best option. From there -   

Single options:  
- Increase cutback to 25% (stil have 0.3 error and 20 year assessment)  
- Increase frequency to 10 years (still have 15% HCR and error = 0.3)  

Combination options:  
- Increase frequency a little (assess = 15 years) + increase cutback a lot (30%)  
- Increase frequency a lot (assess = 5 years) + increase cutback a little (25%)  
- More data (error = 0.1) + smaller increase in fishing (hcr = 0.90) and assessment stays the same (20 years)  
- More data (error = 0.1) + more frequent (assess = 5 years) + increase fishing (hcr = 0.95)  

```{r}
#Step4 Single options

#Step4 - more data:
err4 <- baseline %>%
  filter(error == 0.1) %>% 
  filter(assess == 20) %>% 
  filter(hcr == 0.85) %>% 
  group_by(hcr) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") #all good 

#Step4 - increase cutback:
hcr4 <- baseline %>%
  filter(assess == 20) %>% 
  filter(error == 0.3) %>% 
  filter(hcr == 0.75) %>%
  group_by(hcr) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate(prop_bad = (closed)/(good + closed))

#Step4 - increase frequency: 
assess4 <- baseline %>%
  filter(assess == 10) %>% 
  filter(error == 0.3) %>% 
  filter(hcr == 0.85) %>% 
  group_by(hcr) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate(prop_bad = (closed)/(good + closed)) 

#Step4 - combo 1 increase frequency a little and cutback a lot: 
combo1 <- baseline %>%
  filter(error == 0.3) %>% 
  filter(assess == 15) %>% 
  filter(hcr == 0.70) %>% 
  group_by(hcr) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate(prop_bad = (closed)/(good + closed))

#Step4 - combo 2 increase frequency and cutback a lot: 
combo2 <- baseline %>%
  filter(error == 0.3) %>% 
  filter(assess == 5) %>% 
  filter(hcr == 0.75) %>% 
  group_by(hcr) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate(prop_bad = (closed)/(good + closed))

#Step4 - combo 3 data + increase fishing a little:
combo3 <- baseline %>%
  filter(error == 0.1) %>% 
  filter(assess == 20) %>% 
  filter(hcr == 0.90) %>% 
  group_by(hcr) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate(prop_bad = (closed + over)/(good + over + closed))

#Step4 - combo 4 data + frequency + increase fishing more:
combo4 <- baseline %>%
  filter(error == 0.1) %>% 
  filter(assess == 10) %>% 
  filter(hcr == 0.90) %>% 
  group_by(hcr) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate(prop_bad = (closed)/(good + closed))
```

```{r}
chase_check <- baseline %>% 
  group_by(error, hcr, assess) %>% 
  count(status) %>% 
  spread(key = "status", value = "n") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(prop_bad = (closed + over)/(good + closed + over))
```

